---
title: "Simulated-exposure-scenarios"
author: "Paul Kruse"
date: "2025-07-30"
output: 
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r switches, include=FALSE}
section_exp <- TRUE
section_pop <- TRUE
section_sim <- TRUE
section_dr <- TRUE
section_pre_eq_dr <- TRUE
```

```{r}
library(httk)
library(dplyr)
library(tidyr)
library(data.table)
#library(GeoTox)
library(gganimate)
library(gifski)
library(ggridges)
devtools::load_all()
```

# Time varying exposure scenarios across different populations

We will examine three different exposure scenarios that result in the same overall exposure to a mixture of chemicals. We then simulate different populations to determine how they react to these different exposure scenarios. In addition, we also examine how varying the time-resolution of the exposures affect the "average" member of each population.

## Exposure scenarios

We look at three different scenarios, representing an acute exposure, a periodic exposure, and a constant exposure. In each scenario, the total exposure to the chemical is the same, though the levels are varied to represent different magnitudes of exposure at a given time. In reality, the body will react in real-time to exposures, but these scenarios will have time points given by hourly data. 

The acute exposure is given by $$f(t) = \bigg\{\begin{array}{ll} 0 & t \in [0,1) \\ 100\exp(-t) & t \in [1, 30]\end{array}$$, starting with zero exposure and then experiencing an sudden high exposure that rapidly decays. The periodic exposure is given by $$f(t) = \frac{100}{19.15}|\sin(t)|$$, which follows a sinusoidal pattern with period every $\pi$ days. Finally, the constant exposure is given by $$f(t) = \frac{10}{3}.$$

```{r exposure, eval = section_exp}
time <- seq(from = 0, to = 30, by = 1/24)
dose_a <- c(rep(0, 24), 100*exp(-time[1:697]))
dose_b <- 100/19.15*abs(sin(time))
dose_c <- rep(10/3, length(time))

acute_exposure_matrix <- matrix(c(time, dose_a), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
periodic_exposure_matrix <- matrix(c(time, dose_b), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
constant_exposure_matrix <- matrix(c(time, dose_c), ncol = 2, dimnames = list(NULL, c('time', 'dose')))

ggplot(acute_exposure_matrix, aes(x = time, y = dose, color = 'Acute')) + geom_line() + geom_line(data = periodic_exposure_matrix, aes(color = 'Periodic')) + geom_line(data = constant_exposure_matrix, aes(color =  'Constant')) + scale_color_manual(values = c('#b2182b', '#ef8a62', '#67a9cf'))
```

For our experiments, the exposure is given in mg of chemical, and each exposure provides 100 mg of total exposure over thirty days. 

## Simulated populations

We will simulated several populations, leaning heavily on the functionality provided by the `httk` R package. We will simulate 500 individuals from the age ranges of 20-29, 30-39, 40-49, 50-59, 60-69, 70-79. These individuals will have `httk` parameters prepared for the following chemicals: Pentacholorphenol (87-86-5) and Bisphenol A (80-05-7) referred to from now on as PCP and BPA, respectively. We simulate this for `Normal` and `Obese` populations.

```{r, eval = section_pop}
twenties_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                           agelim_years = c(20, 29),
                                                           weight_category = 'Normal',
                                                           samples = 500,
                                                           set_seed = TRUE,
                                                           seed = 2345)
#thirties_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(30, 39),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
fourties_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                           agelim_years = c(40, 49),
                                                           weight_category = 'Normal',
                                                           samples = 500,
                                                           set_seed = TRUE,
                                                           seed = 2345)
#fifties_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(50, 59),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
#sixties_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(60, 69),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
seventies_pcp <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                            agelim_years = c(70, 79),
                                                            weight_category = 'Normal',
                                                            samples = 500,
                                                            set_seed = TRUE,
                                                            seed = 2345)

twenties_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                           agelim_years = c(20, 29),
                                                           weight_category = 'Normal',
                                                           samples = 500,
                                                           set_seed = TRUE,
                                                           seed = 2345)
#thirties_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(30, 39),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
fourties_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                           agelim_years = c(40, 49),
                                                           weight_category = 'Normal',
                                                           samples = 500,
                                                           set_seed = TRUE,
                                                           seed = 2345)
#fifties_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(50, 59),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
#sixties_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(60, 69),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
seventies_bpa <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                            agelim_years = c(70, 79),
                                                            weight_category = 'Normal',
                                                            samples = 500,
                                                            set_seed = TRUE,
                                                            seed = 2345)
twenties_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                              agelim_years = c(20, 29),
                                                              weight_category = 'Obese',
                                                              samples = 500,
                                                              set_seed = TRUE,
                                                              seed = 2345)
#thirties_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(30, 39),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
fourties_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                              agelim_years = c(40, 49),
                                                              weight_category = 'Obese',
                                                              samples = 500,
                                                              set_seed = TRUE,
                                                              seed = 2345)
#fifties_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(50, 59),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
#sixties_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
#                                           agelim_years = c(60, 69),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
seventies_pcp_ob <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                               agelim_years = c(70, 79),
                                                               weight_category = 'Obese',
                                                               samples = 500,
                                                               set_seed = TRUE,
                                                               seed = 2345)

twenties_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                              agelim_years = c(20, 29),
                                                              weight_category = 'Obese',
                                                              samples = 500,
                                                              set_seed = TRUE,
                                                              seed = 2345)
#thirties_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(30, 39),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
fourties_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                              agelim_years = c(40, 49),
                                                              weight_category = 'Obese',
                                                              samples = 500,
                                                              set_seed = TRUE,
                                                              seed = 2345)
#fifties_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(50, 59),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
#sixties_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
#                                           agelim_years = c(60, 69),
#                                           weight_category = 'Normal',
#                                           samples = 500,
#                                           set_seed = TRUE,
#                                           seed = 2345)
seventies_bpa_ob <- simulate_population_variability_parameters(chem.cas = '80-05-7',
                                                               agelim_years = c(70, 79),
                                                               weight_category = 'Obese',
                                                               samples = 500,
                                                               set_seed = TRUE,
                                                               seed = 2345)


```
We examine a few these different individuals for different age cohorts and chemicals.

```{r, eval=section_pop}
head(twenties_bpa)
head(seventies_bpa)
head(twenties_pcp)
head(seventies_pcp)
head(twenties_bpa_ob)
head(seventies_bpa_ob)
head(twenties_pcp_ob)
head(seventies_pcp_ob)
```

To use these parameters in modelling, we need to add some model-specific parameters. We will use the 'pbtk' model from `httk` and to add the associated missing parameters, we use the function `parametrize_httk()`.

```{r, warning=FALSE, eval=section_pop}
pcp_20_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = twenties_pcp)
#pcp_30_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = thirties_pcp)
pcp_40_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = fourties_pcp)
#pcp_50_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = fifties_pcp)
#pcp_60_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = sixties_pcp)
pcp_70_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = seventies_pcp)

bpa_20_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = twenties_bpa)
#bpa_30_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = thirties_bpa)
bpa_40_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = fourties_bpa)
#bpa_50_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = fifties_bpa)
#bpa_60_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = sixties_bpa)
bpa_70_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = seventies_bpa)

pcp_20_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = twenties_pcp_ob)
#pcp_30_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = thirties_pcp_ob)
pcp_40_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = fourties_pcp_ob)
#pcp_50_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = fifties_pcp_ob)
#pcp_60_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = sixties_pcp_ob)
pcp_70_ob_param <- parametrize_httk(chem.cas = '87-86-5', model = 'pbtk', mcs = seventies_pcp_ob)

bpa_20_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = twenties_bpa_ob)
#bpa_30_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = thirties_bpa_ob)
bpa_40_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = fourties_bpa_ob)
#bpa_50_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = fifties_bpa_ob)
#bpa_60_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = sixties_bpa_ob)
bpa_70_ob_param <- parametrize_httk(chem.cas = '80-05-7', model = 'pbtk', mcs = seventies_bpa_ob)
```

## Exposure simulations

We now simulate exposure through the three scenarios described above, collecting the relevant data from the httk simulations. 

### PCP simulations

We suppress the color scale in this case because with 500 individuals, the guide becomes too unruly.

```{r, warning=FALSE, eval=section_sim}
acute_pcp_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_pcp_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_pcp_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_pcp_ob_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_pcp_ob_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_pcp_ob_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
acute_pcp_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_pcp_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_pcp_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_pcp_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_pcp_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_pcp_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```

Observe that there appears to be some variability in responses to the exposure scenario for the different populations. In general for the normal weight category, the most sensitive individuals among the 20-29 cohort have a peak blood plasma concentration between 1.5 - 2.0, while  for those in the 40-49 cohort the values are from 2.0 - 3.0, and for 70-79 the values are 2.0 - 6.0. For the obese weight category, the most sensitive individuals among the 20 - 29 cohort experience a max Cplasma level between 0.75 - 1.5, for the 40 - 49 cohort between 0.75 - 1.25 with one heavy outlier above 2.0 in this simulation, and for the 70 - 79 cohort between 0.75 - 1.5. The higher bodyweight of the obese category individuals will translate to a lower dose in mg/kg-day, so this trend of lower max Cplasma is not completely unexpected, though the degree to which bodyweight plays a role is not explored here.

We dig into the numerics with the following.

```{r, eval=section_sim}
acute_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(acute_pcp_20$numeric, acute_pcp_40$numeric, acute_pcp_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(acute_pcp_20$numeric, acute_pcp_40$numeric, acute_pcp_70$numeric), function(t) {max(t$AUC)}),
                             Age = rep(c(20, 40, 70), each = 501),
                             BW = c(twenties_pcp$BW, mean(twenties_pcp$BW), fourties_pcp$BW, mean(fourties_pcp$BW), seventies_pcp$BW, mean(seventies_pcp$BW)),
                             Scenario = 'Acute',
                             Weight = 'Normal')

ggplot(acute_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(acute_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

From the density plots, we observe that the older cohorts do have more mass at higher max Cplasma values than the youngest cohort, and similarly the AUC scores have more mass at higher values with increasing age. There is a heavy right tail in the youngest cohort for AUC, potentially more so than for the 40s cohort.

```{r, eval=section_sim}
acute_ob_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(acute_pcp_ob_20$numeric, acute_pcp_ob_40$numeric, acute_pcp_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(acute_pcp_ob_20$numeric, acute_pcp_ob_40$numeric, acute_pcp_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_pcp_ob$BW, mean(twenties_pcp_ob$BW), fourties_pcp_ob$BW, mean(fourties_pcp_ob$BW), seventies_pcp_ob$BW, mean(seventies_pcp_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Acute',
                             Weight = 'Obese')

ggplot(acute_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(acute_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

The trends among the obese weight category follow a similar pattern for max Cplasma distributions between the different age groups, and again there is more of a heavy right tail for the AUC values in the youngest cohort.


We repeat this analysis for the periodic exposure scenario.

```{r, warning=FALSE, eval=section_sim}
periodic_pcp_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_pcp_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_pcp_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_pcp_ob_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_pcp_ob_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_pcp_ob_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)
```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
periodic_pcp_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_pcp_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_pcp_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_pcp_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_pcp_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_pcp_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```

Again observe that there appears to be some variability in responses to the exposure scenario for the different populations. In general, the most sensitive individuals among the 20-29 and 40-49 cohorts have a peak blood plasma concentration between 0.35 - 0.45, while for those in the 70-79 cohort have the values exceeding 0.4. 

We dig into the numerics with the following.

```{r, eval=section_sim}
periodic_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(periodic_pcp_20$numeric, periodic_pcp_40$numeric, periodic_pcp_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(periodic_pcp_20$numeric, periodic_pcp_40$numeric, periodic_pcp_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_pcp$BW, mean(twenties_pcp$BW), fourties_pcp$BW, mean(fourties_pcp$BW), seventies_pcp$BW, mean(seventies_pcp$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Periodic',
                             Weight = 'Normal')

ggplot(periodic_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(periodic_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

In both the AUC and Max Cplasma distirbutions, with increasing age there is increasing mass at higher values.


```{r, eval=section_sim}
periodic_ob_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(periodic_pcp_ob_20$numeric, periodic_pcp_ob_40$numeric, periodic_pcp_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(periodic_pcp_ob_20$numeric, periodic_pcp_ob_40$numeric, periodic_pcp_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_pcp_ob$BW, mean(twenties_pcp_ob$BW), fourties_pcp_ob$BW, mean(fourties_pcp_ob$BW), seventies_pcp_ob$BW, mean(seventies_pcp_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Periodic',
                             Weight = 'Obese')

ggplot(periodic_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(periodic_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```


Finally, we complete the analysis of the constant exposure scenario.

```{r, warning=FALSE, eval=section_sim}
constant_pcp_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_pcp_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_pcp_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_pcp_ob_20 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_pcp_ob_40 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_40_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_pcp_ob_70 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_70_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
constant_pcp_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_pcp_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_pcp_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_pcp_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_pcp_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_pcp_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```

As with the previous exposure scenarios, there appears to be some variability in responses to the exposure scenario for the different populations. For the normal weight category, the most sensitive individuals among the 20-29 cohort have a peak blood plasma concentration between 0.3 - 0.4, while  for those in the 40-49 cohort the values are from 0.35 - 0.45, and for 70-79 the values are 0.4-0.5. For the obese category, the most sensitive individuals among the 20 - 29 cohort have max Cplasma values between 0.2 - 0.3, for the 40 - 49 cohort values between 0.175 - 0.25, and for the 70 - 79 cohort values between 0.2 - 0.3.

We dig into the numerics with the following.

```{r, eval=section_sim}
constant_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(constant_pcp_20$numeric, constant_pcp_40$numeric, constant_pcp_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(constant_pcp_20$numeric, constant_pcp_40$numeric, constant_pcp_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_pcp$BW, mean(twenties_pcp$BW), fourties_pcp$BW, mean(fourties_pcp$BW), seventies_pcp$BW, mean(seventies_pcp$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Constant',
                             Weight = 'Normal')

ggplot(constant_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(constant_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

As in the previous exposure scenarios, there is increasing mass at higher values of Max Cplasma and AUC with increasing age. Note the similarity in the max Cplasma and AUC density plots between the periodic and constant exposures, and the contrast with the acute exposure scenario. In the acute scenario, most of the exposure is front-loaded and happens within the first few days. This results in a higher max Cplasma value than in the periodic and acute scenarios. Interestingly, the AUC values seem to have more mass at higher values under the acute scenario than the other scenarios, which are nearly identical. We show this more clearly in the plot below. The periodic and constant density plots are very similar and overlap while the acute scenario is distinct for each age cohort.

```{r, eval=section_sim}
ggplot(rbind(acute_httk_pcp[-c(501, 1002, 1503),], periodic_httk_pcp[-c(501, 1002, 1503),], constant_httk_pcp[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')

ggplot(rbind(acute_httk_pcp[-c(501, 1002, 1503),], periodic_httk_pcp[-c(501, 1002, 1503),], constant_httk_pcp[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')
```

From the Cplasma curve plots above, observe that the plots from the acute scenario in general approach a concentration of 0 $\mu$Mol while in the periodic and constant scenarios the curves approach a steady state value that is non-trivial. If the dosing scenarios all were to stop at 30 days but the `httk` 'pbtk' simulations continued for a sufficiently long period, the steady state values of the periodic and constant exposures would approach 0 as there would be no more loading of chemical. In this case, the chemical would have been metabolized and excreted or stored in organs so that the AUC values would all converge. However, in the current simulations, only the acute scenario has had sufficient time for this to be observed, so the AUC is higher in the acute scenario than in the periodic and constant exposure scenarios.

```{r, eval=section_sim}
constant_ob_httk_pcp <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(constant_pcp_ob_20$numeric, constant_pcp_ob_40$numeric, constant_pcp_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(constant_pcp_ob_20$numeric, constant_pcp_ob_40$numeric, constant_pcp_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_pcp_ob$BW, mean(twenties_pcp_ob$BW), fourties_pcp_ob$BW, mean(fourties_pcp_ob$BW), seventies_pcp_ob$BW, mean(seventies_pcp_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Constant',
                             Weight = 'Obese')

ggplot(constant_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(constant_ob_httk_pcp[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

The same trends hold among the obese weight category that are observed in the normal weight category for 


```{r, eval=section_sim}
ggplot(rbind(acute_ob_httk_pcp[-c(501, 1002, 1503),], periodic_ob_httk_pcp[-c(501, 1002, 1503),], constant_ob_httk_pcp[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')

ggplot(rbind(acute_ob_httk_pcp[-c(501, 1002, 1503),], periodic_ob_httk_pcp[-c(501, 1002, 1503),], constant_ob_httk_pcp[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')
```

We examine these values identified by body weight and scenario.

```{r, eval=section_sim}
ggplot(rbind(acute_ob_httk_pcp[-c(501, 1002, 1503),], periodic_ob_httk_pcp[-c(501, 1002, 1503),], constant_ob_httk_pcp[-c(501, 1002, 1503),], acute_httk_pcp[-c(501, 1002, 1503),], periodic_httk_pcp[-c(501, 1002, 1503),], constant_httk_pcp[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = interaction(Weight, Scenario), fill = interaction(Weight, Scenario))) + ggridges::geom_density_ridges(alpha = 0.1) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Weight:Scenario', color = 'Weight:Scenario')

ggplot(rbind(acute_ob_httk_pcp[-c(501, 1002, 1503),], periodic_ob_httk_pcp[-c(501, 1002, 1503),], constant_ob_httk_pcp[-c(501, 1002, 1503),], acute_httk_pcp[-c(501, 1002, 1503),], periodic_httk_pcp[-c(501, 1002, 1503),], constant_httk_pcp[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = interaction(Weight, Scenario), fill = interaction(Weight, Scenario))) + ggridges::geom_density_ridges(alpha = 0.1) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Weight:Scenario', color = 'Weight:Scenario')
```

From the analyses of each weight scenario, we have already observed that the periodic and constant scenarios overlap a lot. This is evident by the fact that for each age cohort, there appears to be little difference between these exposure scenarios. Note however that the Obese:Periodic and Obese:Constant distributions are markedly shifted to lower values in both Max Cplasma and AUC than the Normal:Periodic and Normal:Constant. Similarly, the Obese:Acute is concentrated around lower values than Normal:Acute. This is in part explained by the fact that with more mass but with the same exposure that the blood plasma concentrations will be lower in the Obese weight category compared to the normal weight category.

### BPA simulations

We suppress the color scale in this case because with 500 individuals, the guide becomes too unruly.

```{r, warning=FALSE, eval=section_sim}
acute_bpa_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_bpa_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_bpa_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_bpa_ob_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_bpa_ob_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

acute_bpa_ob_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_ob_param, plot = TRUE, data.matrix = acute_exposure_matrix, plot_average = TRUE)

```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
acute_bpa_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_bpa_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_bpa_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_bpa_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_bpa_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_bpa_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```


Observe that there appears to be some variability in responses to the exposure scenario for the different populations. In general for the normal weight category, the most sensitive individuals among the 20-29 cohort have a peak blood plasma concentration between 0.8 - 1.3, while  for those in the 40-49 cohort the values are from 1.0 - 1.6, and for 70-79 the values are 0.8 - 1.2. For the obese weight category, the most sensitive individuals among the 20 - 29 cohort have peak blood plasma concentrations between 0.4 - 0.6, for 40 - 49 between 0.5 - 0.8, and for 70 - 79 between 0.5 - 0.8.

We dig into the numerics with the following.

```{r, eval=section_sim}
acute_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(acute_bpa_20$numeric, acute_bpa_40$numeric, acute_bpa_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(acute_bpa_20$numeric, acute_bpa_40$numeric, acute_bpa_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa$BW, mean(twenties_bpa$BW), fourties_bpa$BW, mean(fourties_bpa$BW), seventies_bpa$BW, mean(seventies_bpa$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Acute',
                             Weight = 'Normal')

ggplot(acute_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(acute_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

From the density plots, we observe that the older cohorts do have more mass at higher max Cplasma values than the youngest cohort, and similarly the AUC scores have more mass at higher values with increasing age.

```{r, eval=section_sim}
acute_ob_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(acute_bpa_ob_20$numeric, acute_bpa_ob_40$numeric, acute_bpa_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(acute_bpa_ob_20$numeric, acute_bpa_ob_40$numeric, acute_bpa_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa_ob$BW, mean(twenties_bpa_ob$BW), fourties_bpa_ob$BW, mean(fourties_bpa_ob$BW), seventies_bpa_ob$BW, mean(seventies_bpa_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Acute',
                             Weight = 'Obese')

ggplot(acute_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(acute_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

The same patterns hold within the obese weight category as in the normal weight category.

We repeat this analysis for the periodic exposure scenario.

```{r, warning=FALSE, eval=section_sim}
periodic_bpa_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_bpa_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_bpa_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_bpa_ob_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_bpa_ob_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

periodic_bpa_ob_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_ob_param, plot = TRUE, data.matrix = periodic_exposure_matrix, plot_average = TRUE)

```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
periodic_bpa_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_bpa_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_bpa_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_bpa_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_bpa_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
periodic_bpa_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```

Again observe that there appears to be some variability in responses to the exposure scenario for the different populations. For the normal weight category, the most sensitive individuals among the 20-29 and 40-49 cohorts have values between 0.08 and 0.12, while for those in the 70-79 cohort have the values between 0.825 and 0.15. For the obese category, the most sensitive individuals among the 20 - 29 and 40 - 49 cohorts have max Cplasma values between 0.05 - 0.07, and for the 70 - 79 cohort values between 0.05 - 0.08.

We dig into the numerics with the following.

```{r, eval=section_sim}
periodic_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(periodic_bpa_20$numeric, periodic_bpa_40$numeric, periodic_bpa_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(periodic_bpa_20$numeric, periodic_bpa_40$numeric, periodic_bpa_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa$BW, mean(twenties_bpa$BW), fourties_bpa$BW, mean(fourties_bpa$BW), seventies_bpa$BW, mean(seventies_bpa$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Periodic',
                             Weight = 'Normal')

ggplot(periodic_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(periodic_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

In both the AUC and Max Cplasma distributions, with increasing age there is increasing mass at higher values.

```{r, eval=section_sim}
periodic_ob_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(periodic_bpa_ob_20$numeric, periodic_bpa_ob_40$numeric, periodic_bpa_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(periodic_bpa_ob_20$numeric, periodic_bpa_ob_40$numeric, periodic_bpa_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa_ob$BW, mean(twenties_bpa_ob$BW), fourties_bpa_ob$BW, mean(fourties_bpa_ob$BW), seventies_bpa_ob$BW, mean(seventies_bpa_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Periodic',
                             Weight = 'Obese')

ggplot(periodic_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(periodic_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

The max Cplasma and AUC distributions have mass concentrated around lower values than the normal weight category counterparts, but do not show much difference overall among the different age cohorts.


Finally, we complete the analysis of the constant exposure scenario.

```{r, warning=FALSE, eval=section_sim}
constant_bpa_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_bpa_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_bpa_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_bpa_ob_20 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_20_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_bpa_ob_40 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_40_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

constant_bpa_ob_70 <- solve_httk_model(chem.cas = '80-05-7', parameters = bpa_70_ob_param, plot = TRUE, data.matrix = constant_exposure_matrix, plot_average = TRUE)

```

We plot the blood plasma concentration curves.

```{r, eval=section_sim}
constant_bpa_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_bpa_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_bpa_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_bpa_ob_20$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_bpa_ob_40$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
constant_bpa_ob_70$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
```

As with the previous exposure scenarios, there appears to be some variability in responses to the exposure scenario for the different populations. For the normal weight category, the most sensitive individuals among the 20-29 cohort have a peak blood plasma concentration between 0.075 - 0.0825, and similarly so for those in the 40-49 cohort, and for 70-79 the values are 0.075 - 0.1. For the obese weight category, the most sensitive individuals across all age cohorts have max Cplasma values between 0.04 - 0.06.

We dig into the numerics with the following.

```{r, eval=section_sim}
constant_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(constant_bpa_20$numeric, constant_bpa_40$numeric, constant_bpa_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(constant_bpa_20$numeric, constant_bpa_40$numeric, constant_bpa_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa$BW, mean(twenties_bpa$BW), fourties_bpa$BW, mean(fourties_bpa$BW), seventies_bpa$BW, mean(seventies_bpa$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Constant',
                             Weight = 'Normal')

ggplot(constant_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(constant_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

As in the previous exposure scenarios, there is increasing max at higher values of Max Cplasma and AUC with increasing age. 

As was the case with PCP, note the similarity in the max Cplasma and AUC density plots between the periodic and constant exposures, and the contrast with the acute exposure scenario. In the acute scenario, most of the exposure is front-loaded and happens within the first few days. This results in a higher max Cplasma value than in the periodic and acute scenarios. Interestingly, the AUC values seem to have more mass at higher values under the acute scenario than the other scenarios, which are nearly identical. We show this more clearly in the plot below. The periodic and constant density plots are very similar and overlap while the acute scenario is distinct for each age cohort. However, unlike with PCP, it is easier to discern differences in the distributions of the periodic and constant exposure scenarios.

```{r, eval=section_sim}
ggplot(rbind(acute_httk_bpa[-c(501, 1002, 1503),], periodic_httk_bpa[-c(501, 1002, 1503),], constant_httk_bpa[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')

ggplot(rbind(acute_httk_bpa[-c(501, 1002, 1503),], periodic_httk_bpa[-c(501, 1002, 1503),], constant_httk_bpa[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')
```

From the Cplasma curve plots above, observe that the plots from the acute scenario in general approach a concentration of 0 $\mu$Mol while in the periodic and constant scenarios the curves approach a steady state value that is non-trivial, much like in the scenarios for PCP. The time to steady-state for PCP in the periodic exposure scenarios appears to be around 15-20 days while for the constant exposure this is appears to be at or above 30 days, since the curves are still noticeably growing rather than leveling off at their steady-state asymptotic limits. However for BPA the periodic exposure, the Cplasma appears to hit a steady-state around 5-6 days for the twenties and forties cohorts and 8-10 days for the seventies cohort. Similarly, the BPA constant exposure Cplasma curves appear to hit steady-state between 10-15 days for all cohorts.

What this suggests is that the populations have a relatively higher ability to clear BPA than PCP and arrive at steady-state earlier. A consequence of this is that the constant exposure scenario has more mass in the max Cplasma density at slightly lower levels than in the periodic scenario. The relatively quick clearance rates level off the curves faster, and within each period of the periodic exposure, there is more chemical exposure front-loaded in the constant scenario than the periodic scenario. This leads the to more of the BPA being metabolized, distributed, and excreted earlier in the period through the constant scenario, so the max Cplasma level is in general a little lower. As with the PCP, the Max Cplasma is higher in general for the acute scenario than for the periodic and constant scenarios. However, the AUC distributions are much closer, again a consequence of the faster arrival to steady state as well as the lower steady state values. If the simulations were to continue long enough for the periodic and constant exposure scenarios to approach steady state of 0 with no additional chemical loading, the time to achieve this would be shorter than in the PCP case because the clearance rate for BPA is higher and consequently the Cplasma concentrations are lower. There is less to clear and what is cleared will clear faster.

```{r, eval=section_sim}
constant_ob_httk_bpa <- data.table(individual = rep(1:501, 3),
                             Cplasma_max = sapply(c(constant_bpa_ob_20$numeric, constant_bpa_ob_40$numeric, constant_bpa_ob_70$numeric), function(t) {max(t$Cplasma)}),
                             AUC = sapply(c(constant_bpa_ob_20$numeric, constant_bpa_ob_40$numeric, constant_bpa_ob_70$numeric), function(t) {max(t$AUC)}),
                             BW = c(twenties_bpa_ob$BW, mean(twenties_bpa_ob$BW), fourties_bpa_ob$BW, mean(fourties_bpa_ob$BW), seventies_bpa_ob$BW, mean(seventies_bpa_ob$BW)),
                             Age = rep(c(20, 40, 70), each = 501),
                             Scenario = 'Constant',
                             Weight = 'Obese')

ggplot(constant_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = Cplasma_max, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
ggplot(constant_ob_httk_bpa[-c(501, 1002, 1503),], aes(x = AUC, y = as.character(Age), color = Age, fill = Age)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Age cohort', color = 'Age cohort')
```

The older cohorts have slightly heavier right tails than the youngest for the max Cplasma and AUC distributions.

```{r, eval=section_sim}
ggplot(rbind(acute_ob_httk_bpa[-c(501, 1002, 1503),], periodic_ob_httk_bpa[-c(501, 1002, 1503),], constant_ob_httk_bpa[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')

ggplot(rbind(acute_ob_httk_bpa[-c(501, 1002, 1503),], periodic_ob_httk_bpa[-c(501, 1002, 1503),], constant_ob_httk_bpa[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = Scenario, fill = Scenario)) + ggridges::geom_density_ridges(alpha = 0.3) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Scenario', color = 'Scenario')
```

Similar to the normal weight distributions, the constant and periodic exposures greatly overlap in the Max Cplasma and AUC distributions and are centered around lower values than the acute exposure distribution.

We examine these values identified by body weight and scenario.

```{r, eval=section_sim}
ggplot(rbind(acute_ob_httk_bpa[-c(501, 1002, 1503),], periodic_ob_httk_bpa[-c(501, 1002, 1503),], constant_ob_httk_bpa[-c(501, 1002, 1503),], acute_httk_bpa[-c(501, 1002, 1503),], periodic_httk_bpa[-c(501, 1002, 1503),], constant_httk_bpa[-c(501, 1002, 1503),]), aes(x = Cplasma_max, y = as.character(Age), color = interaction(Weight, Scenario), fill = interaction(Weight, Scenario))) + ggridges::geom_density_ridges(alpha = 0.1) + xlab('Max Cplasma') + ylab('Age cohort') + labs(fill = 'Weight:Scenario', color = 'Weight:Scenario')

ggplot(rbind(acute_ob_httk_bpa[-c(501, 1002, 1503),], periodic_ob_httk_bpa[-c(501, 1002, 1503),], constant_ob_httk_bpa[-c(501, 1002, 1503),], acute_httk_bpa[-c(501, 1002, 1503),], periodic_httk_bpa[-c(501, 1002, 1503),], constant_httk_bpa[-c(501, 1002, 1503),]), aes(x = AUC, y = as.character(Age), color = interaction(Weight, Scenario), fill = interaction(Weight, Scenario))) + ggridges::geom_density_ridges(alpha = 0.1) + xlab('AUC') + ylab('Age cohort') + labs(fill = 'Weight:Scenario', color = 'Weight:Scenario')
```

Notice again that the Periodic/Constant overlap is present for both weight groups and that these distributions for both max Cplasma and AUC than the acute distributions. Also notice that the obese weight group have distributions centered at lower values than the normal weight group distributions.

## Dose-response

After completing the exposure simulations and determining the internal blood plasma concentrations, one can ask what sort of response these exposure may cause by using bioactivity assay data. Specifically, pairing dose-response data with the internal concentration data allows one to study the potential response from different types of exposure. We use the function `get_active_assays()` to retrieve and format relevant assay data for use in setting hill parameters for dose-response modelling.

We use assay data for PCP that is already loaded from the GeoTox package.

```{r, warning=FALSE, eval=section_dr}
acute_20_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_20_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
acute_20_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_20_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
acute_40_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_40_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
acute_40_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_40_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
acute_70_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_70_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
acute_70_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_exposure_matrix, model_parameters = pcp_70_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)


periodic_20_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_20_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
periodic_20_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_20_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
periodic_40_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_40_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
periodic_40_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_40_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
periodic_70_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_70_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
periodic_70_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = periodic_exposure_matrix, model_parameters = pcp_70_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)

constant_20_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_20_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
constant_20_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_20_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
constant_40_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_40_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
constant_40_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_40_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
constant_70_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_70_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)
constant_70_ob_pcp_sensitivity <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_exposure_matrix, model_parameters = pcp_70_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5') , IR = 1)

```

Next we graph different measures of sensitivity.

First for 20s.

```{r, eval=section_dr}
# Plots for PCP exposure sensitivity for 20s
ggplot(tidyr::pivot_longer(data.table(acute_20_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(acute_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_20_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_20_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

Next for 40s.

```{r, eval=section_dr}
# Plots for PCP exposure sensitivity for 40s
ggplot(tidyr::pivot_longer(data.table(acute_40_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(acute_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_40_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_40_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

Finally for 70s.

```{r, eval=section_dr}
# Plots for PCP exposure sensitivity for 70s
ggplot(tidyr::pivot_longer(data.table(acute_70_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(acute_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_70_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(periodic_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_70_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(constant_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

We also examine the signed differences, which record the differences in magnitude of changes in the dose-response behavior during increases and decreases of the response.

```{r, eval=section_dr}
# Signed sensitivity for PCP scenarios
sensitivity_acute_20_signed_pcp <- tidyr::pivot_longer(data.table(acute_20_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_acute_20_ob_signed_pcp <- tidyr::pivot_longer(data.table(acute_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_acute_40_signed_pcp <- tidyr::pivot_longer(data.table(acute_40_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_acute_40_ob_signed_pcp <- tidyr::pivot_longer(data.table(acute_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_acute_70_signed_pcp <- tidyr::pivot_longer(data.table(acute_70_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_acute_70_ob_signed_pcp <- tidyr::pivot_longer(data.table(acute_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

sensitivity_periodic_20_signed_pcp <- tidyr::pivot_longer(data.table(periodic_20_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_periodic_20_ob_signed_pcp <- tidyr::pivot_longer(data.table(periodic_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_periodic_40_signed_pcp <- tidyr::pivot_longer(data.table(periodic_40_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_periodic_40_ob_signed_pcp <- tidyr::pivot_longer(data.table(periodic_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_periodic_70_signed_pcp <- tidyr::pivot_longer(data.table(periodic_70_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_periodic_70_ob_signed_pcp <- tidyr::pivot_longer(data.table(periodic_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

sensitivity_constant_20_signed_pcp <- tidyr::pivot_longer(data.table(constant_20_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_constant_20_ob_signed_pcp <- tidyr::pivot_longer(data.table(constant_20_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_constant_40_signed_pcp <- tidyr::pivot_longer(data.table(constant_40_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_constant_40_ob_signed_pcp <- tidyr::pivot_longer(data.table(constant_40_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_constant_70_signed_pcp <- tidyr::pivot_longer(data.table(constant_70_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
sensitivity_constant_70_ob_signed_pcp <- tidyr::pivot_longer(data.table(constant_70_ob_pcp_sensitivity[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)
```

```{r, eval=section_dr}
# Plots of signed sensitivity for PCP scenarios 20s
ggplot(sensitivity_acute_20_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_acute_20_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_20_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_20_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_20_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_20_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```



```{r, eval=section_dr}
# Plots of signed sensitivity for PCP scenarios 40s
ggplot(sensitivity_acute_40_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_acute_40_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_40_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_40_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_40_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_40_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```


```{r, eval=section_dr}
# Plots of signed sensitivity for PCP scenarios 70s
ggplot(sensitivity_acute_70_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_acute_70_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_70_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_periodic_70_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_70_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(sensitivity_constant_70_ob_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```

### Varying time resolution 

We also examine how the time-resolution affects the simulations. We work with the acute exposure scenario in the 20 - 29 cohort for both weight designations at 0.1, 1, and 2 day time resolutions.

```{r, warning=FALSE, eval=section_dr}
acute_20_pcp_standard_variability <- time_resolution_variation(chem.cas = '87-86-5', parameters = pcp_20_param, plot = TRUE, C_ext = acute_exposure_matrix, standardize = TRUE, plot_average = TRUE, resolutions = c(.1, 1, 2), sample = 'left')
acute_20_ob_pcp_standard_variability <- time_resolution_variation(chem.cas = '87-86-5', parameters = pcp_20_ob_param, plot = TRUE, C_ext = acute_exposure_matrix, standardize = TRUE, plot_average = TRUE, resolutions = c(.1, 1, 2), sample = 'left')
```

We examine the plots.

```{r, eval=section_dr}
acute_20_pcp_standard_variability$`0.1`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_20_pcp_standard_variability$`1`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_20_pcp_standard_variability$`2`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')

acute_20_ob_pcp_standard_variability$`0.1`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_20_ob_pcp_standard_variability$`1`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')
acute_20_ob_pcp_standard_variability$`2`$plasma_plot + ggplot2::scale_color_discrete(guide = 'none')

```


We examine the AUC sensitivity.

```{r, eval=section_dr}
acute_20_pcp_variability_stats <- data.table('individual' = 1:501,
                                      '0.1' = sapply(acute_20_pcp_standard_variability$`0.1`$numeric, function(t) {max(t$AUC)}),
                                      '1' = sapply(acute_20_pcp_standard_variability$`1`$numeric, function(t) {max(t$AUC)}),
                                      '2' = sapply(acute_20_pcp_standard_variability$`2`$numeric, function(t) {max(t$AUC)}),
                                      'unadjusted' = sapply(acute_pcp_20$numeric, function(t) {max(t$AUC)}))
acute_20_pcp_variability_long <- tidyr::pivot_longer(acute_20_pcp_variability_stats[-501, ], cols = -1)

summary(acute_20_pcp_variability_stats[, 2])
summary(acute_20_pcp_variability_stats[, 3])
summary(acute_20_pcp_variability_stats[, 4])
summary(acute_20_pcp_variability_stats[, 5])

ggplot(acute_20_pcp_variability_long, aes(x = value, y = name, color = name, fill = name)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC value') + labs(fill = 'Time resolution in days', color = 'Time resolution in days')

```

To delve deeper into these distributions of AUC values, we use the Kolmogorov-Smirnov test to determine which of these pairs of distributions may be significantly different.

Acute scenario, normal weight class KS tests.

```{r, eval=section_dr}
ks.test(x = acute_20_pcp_variability_stats$`0.1`, y = acute_20_pcp_variability_stats$unadjusted)
ks.test(x = acute_20_pcp_variability_stats$`1`, y = acute_20_pcp_variability_stats$unadjusted)
ks.test(x = acute_20_pcp_variability_stats$`2`, y = acute_20_pcp_variability_stats$unadjusted)
```


```{r, eval=section_dr}
acute_20_ob_pcp_variability_stats <- data.table('individual' = 1:501,
                                      '0.1' = sapply(acute_20_ob_pcp_standard_variability$`0.1`$numeric, function(t) {max(t$AUC)}),
                                      '1' = sapply(acute_20_ob_pcp_standard_variability$`1`$numeric, function(t) {max(t$AUC)}),
                                      '2' = sapply(acute_20_ob_pcp_standard_variability$`2`$numeric, function(t) {max(t$AUC)}),
                                      'unadjusted' = sapply(acute_pcp_ob_20$numeric, function(t) {max(t$AUC)}))
acute_20_ob_pcp_variability_long <- tidyr::pivot_longer(acute_20_ob_pcp_variability_stats[-501, ], cols = -1)

summary(acute_20_ob_pcp_variability_stats[, 2])
summary(acute_20_ob_pcp_variability_stats[, 3])
summary(acute_20_ob_pcp_variability_stats[, 4])
summary(acute_20_ob_pcp_variability_stats[, 5])

ggplot(acute_20_ob_pcp_variability_long, aes(x = value, y = name, color = name, fill = name)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC value') + labs(fill = 'Time resolution in days', color = 'Time resolution in days')

```

Acute scenario, obese weight category KS tests.

```{r, eval=section_dr}
ks.test(x = acute_20_ob_pcp_variability_stats$`0.1`, y = acute_20_ob_pcp_variability_stats$unadjusted)
ks.test(x = acute_20_ob_pcp_variability_stats$`1`, y = acute_20_ob_pcp_variability_stats$unadjusted)
ks.test(x = acute_20_ob_pcp_variability_stats$`2`, y = acute_20_ob_pcp_variability_stats$unadjusted)
```

And now we tie in both the dose-response and time resolution analysis for PCP. We compute this for the acute scenario, 20 - 29 cohort, normal and obese weight categories.

We compute the effects of varying time resolution on the same chemical exposure scenario for a single chemical.

```{r, warning=FALSE, eval=section_dr}
time_resolution_acute_20_pcp_standard_response <- compute_time_resolution_sensitivity(chem.cas = '87-86-5', C_ext = acute_exposure_matrix, model_parameters = pcp_20_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5'), IR = 1, resolutions = c(0.1, 1, 2), sample = 'left')
time_resolution_acute_20_ob_pcp_standard_response <- compute_time_resolution_sensitivity(chem.cas = '87-86-5', C_ext = periodic_exposure_matrix, model_parameters = pcp_20_ob_param, hill_params = geo_tox_data$dose_response |> fit_hill(assay = 'endp', chem = 'casn') |> dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5'), IR = 1, resolutions = c(0.1, 1, 2), sample = 'left')

```


```{r, eval=section_dr}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

```{r, eval=section_dr}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

Compute the signed sensitivity.

```{r, eval=section_dr}
# Process the data
resolution_sensitivity_acute_20_pcp_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_20_pcp_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_20_pcp_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_pcp_standard_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_acute_20_pcp_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_20_pcp_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_20_pcp_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```


```{r, eval=section_dr}
# Process the data
resolution_sensitivity_acute_20_ob_pcp_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_20_ob_pcp_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_20_ob_pcp_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_acute_20_ob_pcp_standard_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:6][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_acute_20_ob_pcp_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_20_ob_pcp_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_20_ob_pcp_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```

# Pre-equlibrium steady-state dose-response

We now highlight some functions designed to model dose-response in non-steady-state. Traditional dose-response data and curves are representative of steady-state response to constant dosing regimes, with response measured after dosing periods on the order of hours or days. However, with time-varying exposures this response data is not necessarily an accurate reflection of the dynamics. We investigate the dose-response described by the following framework.

Let $R = f(D)$ denote the steady-state dose-response relationship. Let $K$ denote a decay constant and consider the function $$H(D,t) = f(D)\left(1 - e^{-Kt}\right)$$ which combines a time-decay with the usual dose-response relationship. Notice that as time $t \rightarrow \infty$, $H(D,t) \rightarrow f(D)$, so the steady-state behavior is as we expect. To make the decay dependent on the dose, for a ligand and receptor pair let $k_{-}$ and $k_{+}$ denote the dissociation and association constants, respectively. Define $K(D) = k_{-} + k_{+}D$.

Finally, for a time-series of dose data, if the current response at $t$ is given by $R_t$ and the new dose is $D_t$ with duration $\Delta t$, define $$R_{t + \Delta t} = f(D_t) + (R_t - f(D_t))e^{-K(D_t)\Delta t}$$ which we model using the `response_decay_exponential()` function. Observe that for smaller time steps $\Delta t$, larger values of $K(D_t)$ can produce the same decay term, reflective of the idea that higher concentrations are necessary to produce the same response level in the short term that lower concentrations produce in steady-state. 

When the decay term $e^{-K(D_t)\Delta t}$ is close to 1 (for slow decay), the current response $R_t$ decays but dominates the new response $f(D_t)$ provided the is not greater by orders of magnitude. This means that the overall response is lower in value but persists longer. When the decay term is closer to 0 (for fast decay), the new response $f(D_t)$ dominates the current response $f(D_t)$, again provided they are similar order of magnitude. The overall response is higher in this case, but depends more heavily on the steady-state response values of the dosing, and persists for shorter periods of time as the exposure dissipates.

## Exposure scenarios

We define a few higher dose exposures for exemplary purposes.

```{r, eval=section_pre_eq_dr}
time_dr <- seq(from = 0, to = 30, by = 1/24)
time_2 <- seq(from = (30+1/24), to = 60, by = 1/24)
dose_a_low <- c(rep(0, 24), 1E-1*exp(-time_dr[1:697]))
dose_b_low <- 1E-1/19.15*abs(sin(time_dr))
dose_c_low <- rep(1E-2/3, 721)

acute_exposure_matrix_low <- matrix(c(time_dr, dose_a_low), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
periodic_exposure_matrix_low <- matrix(c(time_dr, dose_b_low), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
constant_exposure_matrix_low <- matrix(c(time_dr, dose_c_low), ncol = 2, dimnames = list(NULL, c('time', 'dose')))




dose_a_high <- c(rep(0, 24), 1E5*exp(-time_dr[1:697]))
dose_b_high <- 1E5/19.15*abs(sin(time_dr))
dose_c_high <- rep(1E4/3, 721)

acute_exposure_matrix_high <- matrix(c(time_dr, dose_a_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
periodic_exposure_matrix_high <- matrix(c(time_dr, dose_b_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
constant_exposure_matrix_high <- matrix(c(time_dr, dose_c_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))

dose_a_very_high <- c(rep(0, 24), 1E11*exp(-time_dr[1:697]))
dose_b_very_high <- 1E11/19.15*abs(sin(time_dr))
dose_c_very_high <- rep(1E10/3, 721)

acute_exposure_matrix_very_high <- matrix(c(time_dr, dose_a_very_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
periodic_exposure_matrix_very_high <- matrix(c(time_dr, dose_b_very_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
constant_exposure_matrix_very_high <- matrix(c(time_dr, dose_c_very_high), ncol = 2, dimnames = list(NULL, c('time', 'dose')))
```

## Simulations

Next we look simulate the internal dynamics of a person in their 20s exposed to PCP.

```{r, eval=section_pre_eq_dr}
single_person_1 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(periodic_exposure_matrix_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_2 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(acute_exposure_matrix_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_3 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(constant_exposure_matrix_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_4 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(periodic_exposure_matrix_very_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_5 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(acute_exposure_matrix_very_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_6 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(constant_exposure_matrix_very_high, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_7 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(periodic_exposure_matrix_low, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_8 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(acute_exposure_matrix_low, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
single_person_9 <- solve_httk_model(chem.cas = '87-86-5', parameters = pcp_20_param[1,], plot = TRUE, data.matrix = rbind(constant_exposure_matrix_low, matrix(c(time_2, rep(0, length(time_2))), ncol = 2, dimnames = list(NULL, c('time', 'dose')))), plot_average = TRUE, keep_all_columns = TRUE)
```

Examine ths summary statistics of the concentrations.

```{r, eval=section_pre_eq_dr}
summary(single_person_1$numeric$`Person 1`)
summary(single_person_2$numeric$`Person 1`)
summary(single_person_3$numeric$`Person 1`)
summary(single_person_4$numeric$`Person 1`)
summary(single_person_5$numeric$`Person 1`)
summary(single_person_6$numeric$`Person 1`)
```
## Assay and Dose Response

We collect assay data.

```{r, eval=section_pre_eq_dr}
# Relevant Hill parameters for different assays
assay_hill_params <- GeoTox::geo_tox_data$dose_response |>
  GeoTox::fit_hill(assay = 'endp', chem = 'casn') |>
  dplyr::filter(!tp.sd.imputed, !logAC50.sd.imputed, chem == '87-86-5')

# Choose assay to use
tox21_dt40_657 <- assay_hill_params[4,]
```

We plot various dose response scenarios using different values for $k_{-}$ and $k_{+}$ that control the dose-dependent decay.

Note that $k_{-}$ and $k_{+}$ are at M level while the output of the blood plasma concentrations max out are around 1E2 uM for high scenarios and 1E8 for very high scenarios. Hence, setting $k_{-}$ = 1E-7 and varying $k_{+}$ from 1E-5 to 1E1 produces values of $K$ ranging from 1E-7 to 1E-3 for high scenarios and 1E-3 to 1E3 for very high scenarios. Moreover, since the timesteps are in terms of seconds while the time-series is given in units of days, the decay is scaled by 8.64E4, so the exponential term is on the order of exp(-1E-3) to exp(-1E1) (exp(-1) to exp(-1E7)) for high (very high), with the latter values representing very fast decay while the former represents slower decay. We expect the fast decay to resemble the response given by the traditional dose-response relationship, while the slow decay will have a lower peak value  but will accumulate response and persist longer at levels above baseline.

First we examine the high periodic exposure scenario.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```

We also observe the decay statistics. 

```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```



Next we examine the very high periodic exposure scenario.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```
Again, we observe the decay statistics. 

```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```


Then the high acute exposure scenario.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```

The corresponding decay statistics. 


```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```

And next the very high acute exposure scenario.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```

And again the decay statistics.


```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```


And finally the high constant exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```
The corresponding decay statistics.


```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```


And the very high constant exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1), aes(time, response)) + geom_point() + geom_line()
```
And the decay statistics.


```{r}
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay > 0, 1-decay])
summary(data.table(response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay > 0, 1-decay])
```
We make some observations. In the above sets of decay statistics, the term 1 - decay corresponds to $1 - e^{-K(D_t)\Delta t}$, which scales the response term of the dose at time $t$, that is $f(D_t)$. When this value is above 1E-2, the plots above show behavior that follows the steady-state dose response curve for each dose. When the decay term is below 1E-3 however, the behavior of this dose-response model more closely resembles a cumulative summation of the steady-state dose response values scaled by the decay term, that is $\sum f(D_t)(1-e^{-K(D_t)\Delta t})$. This difference in behavior appears to be driven by how much of the response from the previous timestep is degraded by the decay relative to how much the update is degraded. This gives a rough idea of what behavior one might expect given the summary statistics of the blood plasma concentrations, the association and dissociation constants, and the time steps. By completing a rough estimate based on orders of magnitude, one can surmise whether the pre-equilibrium behavior will resemble the steady-state model, the scaled summation, or somewhere between.

Observe the decay constant and relation between the response level modeled by the pre-equilibrium method and the sum of responses scaled by the decay term.

```{r}
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-6))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-6))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[, sum(response_addition*(1-decay))]
```
```{r}
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-6))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-6))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[, sum(response_addition*(1-decay))]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[, sum(response_addition*(1-decay))]



```
We see that for the decay values corresponding to less than 1E-3, the computed response and the scaled summation estimate are within an order of magnitude of each other, but above 1E-3, these values diverge considerably. On the flip side, when the decay values are above 1- 1E-3, the computed value and the scaled final dose-response value are incredibly close.


```{r}
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[.N, response_addition*(1-decay)]
```

```{r}
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[.N, response_addition*(1-decay)]

data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[.N, response]
data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[.N, response_addition*(1-decay)]
```
To quanitfy the decay value distribution a bit more, see the output of the chunk below.

```{r}
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E2))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[decay>0,decay], c(0.01, .99))

```

```{r}
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-1))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E2))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E3))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E4))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E5))[decay>0,decay], c(0.01, .99))
quantile(data.table(response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E6))[decay>0,decay], c(0.01, .99))

```
A simple calculation to capture the behavior of a given scenario is $e^{(-(\text{K}(\bar{D})\times 300))}$ where $\bar{D}$ is the mean blood plasma concentration. This decay represents the decay that takes place in 5 minutes. If this is above 1 - 1E-3, the behavior tends toward the scaled summation and if this is below 1E-3, it tends towards the tradition dose-response. Between these values, the behavior is in the transition between the two distinct behaviors.

## Response levels

We can also determine for how long the response is above a given set of thresholds. This is useful for quantifying the cumulative damage associated with exceedance of certain response levels.

First for the high periodic exposure.

```{r, eval=section_pre_eq_dr}
thresholds_periodic <- c('zero' = 0, 'low' = 1E-6, 'medium' = 1E-5, 'high' = 3E-5, 'very high' = 5E-5)

threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_1$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```

Thresholds for high acute exposure.

```{r, eval=section_pre_eq_dr}
thresholds_acute <- c('zero' = 0, 'low' = 1E-5, 'medium' = 1E-4, 'high' = 2E-4)

threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_2$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```

And thresholds for high constant exposure.

```{r, eval=section_pre_eq_dr}
thresholds_constant <- c('zero' = 0, 'low' = 1E-6, 'medium' = 1E-5, 'high' = 5E-5)

threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_3$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```


Observe that the total response AUC in all three exposure scenarios is lower for the slower decay than the faster decay (1.47E-3 vs 2.83E-3 in periodic, 1.89E-3 vs 2.93E-3 in acute, 1.47E-3 vs 2.83E-3 in constant). Similarly, response levels are higher in the faster decay scenarios than the slower decay scenarios. The transition between slow decay and fast decay also presents some interesting behavior. While there is a trend that higher threshold values are exceeded longer for fast decay speed compared to slow decay speed, the time exceeded and response sum above the thresholds actually peak for mid-range decay speed. This intuitively makes sense since the decay speed controls a tradeoff between peak response level and decay of response. Very slow decay peaks at lower values and remains above baseline longer while very fast decay peaks higher but decays faster. The middle ground of mid-range response decay will peak in between, but also remain at elevated levels longer. 

We repeat for the very high exposure scenarios.

First for the very high periodic exposure.

```{r, eval=section_pre_eq_dr}
thresholds_periodic <- c('zero' = 0, 'low' = 1, 'medium' = 1E1, 'mid' = 3E1, 'high' = 5E1, 'very high' = 1E2)

threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_periodic, response_data = response_decay_exponential(plasma_data = single_person_4$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```

Thresholds for very high acute exposure.

```{r, eval=section_pre_eq_dr}
thresholds_acute <- c('zero' = 0, 'low' = 1, 'medium' = 1E1, 'mid' = 3E1, 'high' = 5E1, 'very high' = 1E2)

threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_acute, response_data = response_decay_exponential(plasma_data = single_person_5$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```

And thresholds for very high constant exposure.

```{r, eval=section_pre_eq_dr}
thresholds_constant <- c('zero' = 0, 'low' = 1, 'medium' = 1E1, 'mid' = 3E1, 'high' = 5E1, 'very high' = 1E2)

threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-5))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-3))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E-2))
threshold_exceedance(thresholds = thresholds_constant, response_data = response_decay_exponential(plasma_data = single_person_6$numeric$`Person 1`, max = tox21_dt40_657$resp_max, AC50 = 10^tox21_dt40_657$logAC50, n = 1, k_off = 2.5E-7, k_on=1.4E1))
```

In the case of very high exposure scenarios, the decay rates are all relatively fast given the magnitude of the blood plasma concentrations and the association constant. Hence, there is little difference in the various combinations of decay constant values and times exceeding different thresholds. However, it is clear that the time exceeding thresholds and sum of response over those thresholds does differ by scenario. For instance, the overall response sum for lower thresholds (0, 1) is higher in the periodic and constant exposure scenarios than the acute exposure scenario and similarly for mid range thresholds (1E1). Also of note, the acute exposure has higher time exceeding higher thresholds (5E1) than the periodic and constant exposure scenarios.

## Variations in dose response due to binding kinetics

Since $K_D = \frac{k_{\text{off}}}{k_{\text{on}}}$, there are pairs of kinetic parameters of varying orders of magnitude that produce the same $K_D$ value. We will vary these parameters to produce several different values of $K_D$ and examine how these affect the time-dependent dose response for a fixed exposure scenario. 

To simplify these calculations, we will assume an equilibrium dose response curve that has the following parameters: resp_max = 100, logAC50 = -3, and n = 1.

We will examine $K_D$ values of 1E-15, 1E-14, 1E-13, 1E-12, 1E-11, 1E-10. For each of these, we set $K_{\text{on}}$ to be 1E2, 1E3, 1E4, 1E5, and 1E6, which determines the values of $K_{\text{off}}$.

### K_off 1E-9, K_D 1E-11 to 1E-15

Periodic low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E6), aes(time, response)) + geom_point() + geom_line()
```

Acute low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E6), aes(time, response)) + geom_point() + geom_line()
```

Constant low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-9, k_on=1E6), aes(time, response)) + geom_point() + geom_line()
```


### K_off 1E-10, K_D 1E-11 to 1E-15

Periodic low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```

Acute low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```

Constant low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-10, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```

### K_off 1E-11, K_D 1E-12 to 1E-16

Periodic low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_7$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```

Acute low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_8$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```

Constant low exposure.

```{r, eval=section_pre_eq_dr}
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E1), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E2), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E3), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E4), aes(time, response)) + geom_point() + geom_line()
ggplot(response_decay_exponential(plasma_data = single_person_9$numeric$`Person 1`, max = 100, AC50 = 10^(-3), n = 1, k_off = 1E-11, k_on=1E5), aes(time, response)) + geom_point() + geom_line()
```
```{r}
devtools::session_info()
```
