---
title: "Time-dependent GeoTox"
output: html_document
date: "2025-06-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(httk)
library(dplyr)
library(tidyr)
library(data.table)
library(GeoTox)
library(gganimate)
library(gifski)
devtools::load_all()
```

#Time Dependent GeoTox

This is an introduction and brainstorming document for creating a time-dependent GeoTox object and tailoring functions to use this object.

## Exposure Object

Create the GeoTox object `GT`.

```{r}
GT <- GeoTox::GeoTox()
```


The exposure object will have columns `Location`, `Chemical`, `Time`, `Exposure` plus potentially other columns.

```{r}
exposure_td <- data.frame(Location = rep(c('CT', 'NC'), each = 6), Chemical = rep(paste0('chem',1:3), 4), casn = rep(paste0('casn', 1:3), 4), Time = rep(rep(1:2, each = 3), 2), Exposure = 1:12)
```

Assign a new list value to the GeoTox object under the name `exposure_td`.

```{r}
GT$exposure_td <- exposure_td
GT$exposure_td
```

In the function `GeoTox::simulate_population()`, the list value `C_ext` is assigned to `GT` using the `GeoTox::simulate_exposure()` function. We already have exposure data with external concentrations, so we split the values by location and chemical.

```{r}
GT$C_ext <- lapply(split(GT$exposure_td, ~Location), function(df) {
  split(df, ~ Chemical)
})
GT$C_ext
```
Note that the exposure data is organized first by location and then by chemical. So to recover data for chem3 in CT we would use `GT$C_ext$CT$chem3`. 

## Preparing `httk` models

With time series exposure data for each chemical and location, we now can use the various `httk::solve_*` functions to run simulations on the exposure. 

We need to parameterize the model we wish to use from httk. To do this, we first generate populate parameters using the following function. This needs to be run for each chemical, age limit, and weight category. This could be completed in the `GeoTox::simulate_population()` function. These would then be stored in `GT$httk_param`, nested in the same manner as other new features, by location, chemical. We could `rbind` all outputs across `agelim_years` and `weight_category` values for one table per location-chemical pair. In this example, we simulate 100 people with ages from 21 to 30 in the weight category 'Normal' (as opposed to the alternate 'Obese' option). We also set a seed for reproducibility.

```{r}
pop_param <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                           agelim_years = c(21, 30),
                                           weight_category = 'Normal',
                                           samples = 100,
                                           set_seed = TRUE,
                                           seed = 2345)
head(pop_param)
```

Note, if you would like to simulate a population with specific number of people for different ages, this can be done as well.

```{r}
age_matrix <- matrix(c(3, 21, 43, 2, 4, 2), ncol = 2)
colnames(age_matrix) <- c('age', 'samples')
pop_param_2 <- simulate_population_variability_parameters(chem.cas = '87-86-5',
                                                          weight_category = 'Normal',
                                                          age_matrix = age_matrix,
                                                          set_seed = TRUE,
                                                          seed = 2345)
head(pop_param_2)
```


Once we have these parameters, we pick a model from httk, in this case 'pbtk', and input the population parameters. This prepares parameters for each person of the simulated population that can then be used in the `httk::solve_pbtk` function.

```{r}
pbtk_param <- parametrize_httk(chem.cas = '87-86-5',
                               model= 'pbtk',
                               mcs = pop_param)
```


We will also need to convert `C_ext` data from external dosing to internal dosing. Using the existing functions, we can augment the `C_ext` data as follows. Here we assume the `IR` parameter is 3.2 just to illustrate the method. One thing to note is that we depending on the time resolution, the `time` parameter may also need input. In this case, using `purrr::map2` may be the more appropriate function for this task. This calculation might also involve using the `diff` function to determine time intervals with a decision made on how best to determine the time period for the last exposure value when the exposure events are not at equally spaced times. Finally, body weight is not currently input into this example function, but should in the future.

```{r}
GT$D_ext <- lapply(GT$C_ext, function(l){
  lapply(l, function(df){
    df |> dplyr::mutate(Dose = calc_internal_dose(matrix(.data$Exposure),
                                           IR = 3.2)[[1]])})
  })
GT$D_ext
```



In the following examples, we will use a dose matrix that spans 30 days of data, with an acute exposure given by the function 100exp(-t) for t in days, broken up by hour. The exposure is 0 for the first day and then follows the function as described. The area under the curve is approximately 100. We also have a periodic exposure given by 100/19*abs(sin(t)), and a constant exposure given by 10/3. Time is measured in days and exposure is measured in 'mg/kg', which we can change.

```{r}
time <- seq(0, 30, 1/24)
dose_a <- c(rep(0, 24), 100*exp(-time[1:697]))
acute_dose_matrix <- matrix(c(time, dose_a), ncol = 2)
colnames(acute_dose_matrix) <- c('time', 'dose')

dose_b <- 100/19*abs(sin(time))
periodic_dose_matrix <- matrix(c(time, dose_b), ncol = 2)
colnames(periodic_dose_matrix) <- c('time', 'dose')

dose_c <- rep(10/3, length(time))
constant_dose_matrix <- matrix(c(time, dose_c), ncol = 2)
colnames(constant_dose_matrix) <- c('time', 'dose')
```

Finally, we simulate the chemical adme with the population parameters and dosing matrix. We also generate a plot of the simulations.

The acute exposure.

```{r}
simulation_acute <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = acute_dose_matrix, standardize = FALSE)
#head(simulation_acute$numeric)
simulation_acute$plasma_plot
```

The periodic exposure.

```{r}
simulation_periodic <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = periodic_dose_matrix, standardize = FALSE)
#head(simulation_periodic$numeric)
simulation_periodic$plasma_plot
```

The constant exposure.

```{r}
simulation_constant <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = constant_dose_matrix, standardize = FALSE)
#head(simulation_constant$numeric)
simulation_constant$plasma_plot
```
One thing to note is that as written, this is simulating the same dosing level for each person, while in reality the same exposure level will represent different dosing levels based on age, weight. This should be accounted for by taking the dosing matrix, using the inhalation rate for that simulated person, and adjusting the internal dose to 'mg/kg' based on the weight of the simulated person. This would be built into the step during which we calculate and assign values to `GT$D_ext`. How best to do this is to be determined.

We repeat the above plots with the same overall dose for each person, in 'mg' rather dose rate 'mg/kg'.

The acute exposure.

```{r}
simulation_acute_fixed_dose <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = acute_dose_matrix, input.units = 'mg', standardize = FALSE)
#head(simulation_acute$numeric)
simulation_acute_fixed_dose$plasma_plot
```

The periodic exposure.

```{r}
simulation_periodic_fixed_dose <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = periodic_dose_matrix, input.units = 'mg', standardize = FALSE)
#head(simulation_periodic$numeric)
simulation_periodic_fixed_dose$plasma_plot
```

The constant exposure.

```{r}
simulation_constant_fixed_dose <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = constant_dose_matrix, input.units = 'mg', standardize = FALSE)
#head(simulation_constant$numeric)
simulation_constant_fixed_dose$plasma_plot
```
Finally, we demonstrate the simulation with dosing standardized to the time segment between dosing time points and with the inhalation rate determined by body weight. The dosing units are 'mg/kg'.

The acute exposure.

```{r}
simulation_acute_standard <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = acute_dose_matrix, standardize = TRUE)
#head(simulation_acute_standard$numeric)
simulation_acute_standard$plasma_plot
```

The periodic exposure.

```{r}
simulation_periodic_standard <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = periodic_dose_matrix, standardize = TRUE)
#head(simulation_periodic_standard$numeric)
simulation_periodic_standard$plasma_plot
```

The constant exposure.

```{r}
simulation_constant_standard <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = constant_dose_matrix, standardize = TRUE)
#head(simulation_constant_standard$numeric)
simulation_constant_standard$plasma_plot
```

Finally, we may look at the 'average' person among the population. To do this, we use the `get_population_statistics()` function to process the average person among the simulated people. This takes the average value for each population parameter.

```{r}
average_person <- get_population_statistics(pbtk_param)
average_person
```
We can also plot this average person with the general population.

The acute exposure.

```{r}
simulation_acute_standard_average <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = acute_dose_matrix, standardize = TRUE, plot_average = TRUE)
#head(simulation_acute_standard_average$numeric)
simulation_acute_standard_average$plasma_plot
```

The periodic exposure.

```{r}
simulation_periodic_standard_average <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = periodic_dose_matrix, standardize = TRUE, plot_average = TRUE)
#head(simulation_periodic_standard_average$numeric)
simulation_periodic_standard_average$plasma_plot
```

The constant exposure.

```{r}
simulation_constant_standard_average <- solve_httk_model(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, data.matrix = constant_dose_matrix, standardize = TRUE, plot_average = TRUE)
#head(simulation_constant_standard_average$numeric)
simulation_constant_standard_average$plasma_plot
```


### Plotting time-series exposure and response

We also can leverage the time evolution of the data using chloropleth plots that we then animate. We build the prototype function below and test it out. First we create some mock time-series data. There are five counties, three with complete data and two with incomplete data.


```{r}
mock_time_series <- data.frame(FIPS = rep(c(37001, 37003, 37181, 37135, 37063), each = 10), casn = rep(c('87-86-5'), 50), chnm = rep(c('Pentachlorophenol'), 50), Time = rep(c(1990:1999), 5), Exposure = c(1:10, 10:1, c(3, 5, 7, 9, 15, 25), rep(NA, 4), rep(NA, 5), c(2,2,3), rep(NA, 2), seq(3, 7, length.out = 10)))
mock_time_series
```

We process this data following a similar approach to what is already use in the GeoTox package.


```{r}
sf_data_nc <- tibble::tibble("_temp_join_id_" = names(split(mock_time_series, ~FIPS)), data = split(mock_time_series, ~FIPS)) |> 
    tidyr::unnest(cols = "data") |> 
    dplyr::inner_join(geo_tox_data$boundaries$county |> dplyr::rename("_temp_join_id_" = 1),
                      by = dplyr::join_by("_temp_join_id_")) |> 
    dplyr::select(-"_temp_join_id_") |> 
    dplyr::mutate(dplyr::across(tidyselect::any_of('chnm'),
                                ~ stringr::str_remove_all(., "\u200b"))) |> sf::st_as_sf()
```

Next we construct the chloropleth and animate it using the `gganimate` R package. In this example, county borders are colored white, counties without any data are colored light grey, and counties with incomplete data are color grey95 at times when missing data. For counties and times with data, the color is determined by a normalized viridis scale.

```{r}
nc_movie <- ggplot() + geom_sf(data= geo_tox_data$boundaries$state, aes(geometry = geometry), fill = NA, size = 0.15) + 
  geom_sf(data = sf_data_nc, aes(fill = Exposure, geometry = geometry), color = 'white') + geom_sf(data = geo_tox_data$boundaries$county |> dplyr::filter(!(FIPS %in% sf_data_nc$FIPS)), ggplot2::aes(geometry = .data$geometry), fill = 'light grey', color = 'white', lwd = 0.01)
nc_movie <- nc_movie +
    ggplot2::scale_fill_viridis_c(
      name = "Normalized\nConcentration",
      direction = -1,
      option = "A",
      limits = c(0, max(sf_data_nc$Exposure, na.rm = TRUE)),
      na.value = 'grey95') +
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.ticks = ggplot2::element_blank(),
      axis.text = ggplot2::element_blank(),
      strip.text = ggplot2::element_text(size = 6),
      text = ggplot2::element_text(size = 12),
      panel.grid.major = ggplot2::element_blank(),
      panel.grid.minor = ggplot2::element_blank()) + labs(title = 'Exposure at time {frame_time}')
nc_movie <- nc_movie + gganimate::transition_time(Time, range = c(1990L, 1999L))
gganimate::animate(nc_movie, nframes = 10, fps = 1)
```

The sensitivity analysis currently used by GeoTox simulates exposure or uses the stored exposure values. With time-dependent exposure, it may be better to sample from the empirical distribution determined by the exposure data for a given time resolution. This will give `C_ext` values to use within the `compute_sensitivity()` function. Alternatively, instead of using an empirical distribution, one could consider sampling uniformly from the range of exposure values represented by the exposure data as the empirical distribution may correspond to a rare event while the uniform sampling represents a portion of the potential values that are possible.

We begin to formulate the sensitivity due to the external exposure. We compute this by fixing all parameters aside from the external dose, using the 'average' individual among a population of individuals, and examining the effects of the external dose on the blood plasma concentrations and in turn how these affect the dose-response. First, we take determine the average person among the population parameters. Then we run the appropriate httk model on this person, using the external dosing information. The function computes the internal dose and solves the time-dependent httk model on this. We take the blood plasma concentrations from this and use these values for the dose-response. Next, hill parameters associated to the chemical and a given assay are supplied and the dose-response curves are calculated from the internal plasma concentrationvalues. Now, if we were to use this dose-response data as is, the response will follow a similar pattern as the exposure. Instead, we are looking at the incremental changes of the dose-response according to the fixed change in plasma concentration, so we take the absolute value of the incremental differences of the responses.

```{r}
# Example Hill parameters are not necessarily realistic
hill_params_pcp <- fit_hill(data.frame(chem = rep(c("87-86-5"), 3),
                                   logc = c(0, 1, 2),
                                   resp = c(4, 2, 0) / 10),
                        chem = "chem")

hill_params_bpa <- fit_hill(data.frame(chem = rep(c("87-86-5"), 3),
                                   logc = c(-1, 0, 1),
                                   resp = c(10, 5, 0) / 10),
                        chem = "chem")


hill_params_mix <- fit_hill(data.frame(chem = rep(c("87-86-5", "80-05-7"), each = 3),
                                   logc = c(-1, 0, 1, 0, 1, 2),
                                   resp = c(10, 5, 0, 4, 2, 0) / 10),
                        chem = "chem")

mixture_c_ext <- cbind(acute_dose_matrix, periodic_dose_matrix[, 2])
dimnames(mixture_c_ext) <- list(NULL, c('time', '87-86-5', '80-05-7'))

# Sensitivity for Pentacholorphenol (PCP) 87-86-5 using three exposure scenarios
td_sensitivity_acute_pcp <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = acute_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_pcp, IR = 1)
td_sensitivity_periodic_pcp <- compute_c_ext_sensitivity(chem.cas = c('87-86-7'), C_ext = periodic_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_pcp, IR = 1)
td_sensitivity_constant_pcp <- compute_c_ext_sensitivity(chem.cas = c('87-86-5'), C_ext = constant_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_pcp, IR = 1)

# Sensitivity for Bisphenol A (BPA) 80-05-7 using same three exposure scenarios
td_sensitivity_acute_bpa <- compute_c_ext_sensitivity(chem.cas = c('80-05-7'), C_ext = acute_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1)
td_sensitivity_periodic_bpa <- compute_c_ext_sensitivity(chem.cas = c('80-05-7'), C_ext = periodic_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1)
td_sensitivity_constant_bpa <- compute_c_ext_sensitivity(chem.cas = c('80-05-7'), C_ext = constant_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1)

# Sensitivity for PCP under acute exposure scenario and BPA under periodic exposure scenario
td_sensitivity_mixture <- compute_c_ext_sensitivity(chem.cas = c('87-86-5', '80-05-7'), C_ext = mixture_c_ext, model_parameters = pbtk_param, hill_params = hill_params_mix, IR = 1)


# Plots for PCP exposure sensitivity
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_acute_pcp[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_periodic_pcp[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_constant_pcp[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# Plots for BPA exposures sensitivity
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_acute_bpa[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_periodic_bpa[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() +
  xlab('log10 absolute difference in response')
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_constant_bpa[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# Plot for mixture exposure scenario (Acute for PCP and Periodic for BPA)
ggplot(tidyr::pivot_longer(data.table(td_sensitivity_mixture[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')







```

For a signed version of this, to differentiate increases from decreases in the response curve, we can do the following.

```{r}
# Signed sensitivity for PCP scenarios
td_sensitivity_acute_signed_pcp <- tidyr::pivot_longer(data.table(td_sensitivity_acute_pcp[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

td_sensitivity_periodic_signed_pcp <- tidyr::pivot_longer(data.table(td_sensitivity_periodic_pcp[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

td_sensitivity_constant_signed_pcp <- tidyr::pivot_longer(data.table(td_sensitivity_constant_pcp[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Signed sensitivity for BPA scenarios
td_sensitivity_acute_signed_bpa <- tidyr::pivot_longer(data.table(td_sensitivity_acute_bpa[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

td_sensitivity_periodic_signed_bpa <- tidyr::pivot_longer(data.table(td_sensitivity_periodic_bpa[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

td_sensitivity_constant_signed_bpa <- tidyr::pivot_longer(data.table(td_sensitivity_constant_bpa[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Signed sensivity for mixture scenario
td_sensitivity_mixture_signed <- tidyr::pivot_longer(data.table(td_sensitivity_mixture[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)


# Plots of signed sensitivity for PCP
ggplot(td_sensitivity_acute_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(td_sensitivity_periodic_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(td_sensitivity_constant_signed_pcp, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)

# Plots of signed sensitivity for BPA
ggplot(td_sensitivity_acute_signed_bpa, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(td_sensitivity_periodic_signed_bpa, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(td_sensitivity_constant_signed_bpa, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)

# Plot of signed sensitivity for mixture
ggplot(td_sensitivity_mixture_signed, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```

We also can examine how sensitive the simulations are to changes in the time resolution. While more frequent readings of ambient air concentrations support more accurate modelling efforts, one may be limited to less frequent readings. How the differences in time resolution impact the blood-plasma concentration and in turn the dose response may in turn inform what time resolution is required for accurate modelling. 

We examine the acute, periodic, and constant exposure scenarios under different time resolutions to determine the effects of these resolutions on the plasma concentration values. Note that in each of these scenarios, the time resolution is by the hour, so roughly 0.0416 days. We examine the resolutions of .1, 1, and 2 days.

```{r}
acute_standard_variability <- time_resolution_variation(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, C_ext = acute_dose_matrix, standardize = TRUE, plot_average = TRUE, resolutions = c(.001, .01, .1, 1, 2), sample = 'left')

periodic_standard_variability <- time_resolution_variation(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, C_ext = periodic_dose_matrix, standardize = TRUE, plot_average = TRUE, resolutions = c(.001, .01, .1, 1, 2), sample = 'left')
  
constant_standard_variability <- time_resolution_variation(chem.cas = '87-86-5', parameters = pbtk_param, plot = TRUE, C_ext = constant_dose_matrix, standardize = TRUE, plot_average = TRUE, resolutions = c(.001, .01, .1, 1, 2), sample = 'left')
```
We examine the plots. First the acute exposure scenario.

```{r}
acute_standard_variability$`0.1`$plasma_plot
acute_standard_variability$`1`$plasma_plot
acute_standard_variability$`2`$plasma_plot
```

The periodic scenario.

```{r}
periodic_standard_variability$`0.1`$plasma_plot
periodic_standard_variability$`1`$plasma_plot
periodic_standard_variability$`2`$plasma_plot
```

And the constant scenario.

```{r}
constant_standard_variability$`0.1`$plasma_plot
constant_standard_variability$`1`$plasma_plot
constant_standard_variability$`2`$plasma_plot
```
We can dig further into the data by looking at the AUC of each person in each time resolution and exposure scenario. We compare with the original run without time resolution modification.

First for the acute scenario.

```{r}
acute_variability_stats <- data.table('individual' = 1:101,
                                      '0.1' = sapply(acute_standard_variability$`0.1`$numeric, function(t) {max(t$AUC)}),
                                      '1' = sapply(acute_standard_variability$`1`$numeric, function(t) {max(t$AUC)}),
                                      '2' = sapply(acute_standard_variability$`2`$numeric, function(t) {max(t$AUC)}),
                                      'unadjusted' = sapply(simulation_acute_standard_average$numeric, function(t) {max(t$AUC)}))
acute_variability_long <- tidyr::pivot_longer(acute_variability_stats, cols = -1)

summary(acute_variability_stats[, 2])
summary(acute_variability_stats[, 3])
summary(acute_variability_stats[, 4])
summary(acute_variability_stats[, 5])

ggplot(acute_variability_long, aes(x = value, y = name, color = name, fill = name)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC value') + labs(fill = 'Time resolution in days', color = 'Time resolution in days')

```
To delve deeper into these distributions of AUC values, we use the Kolmogorov-Smirnov test to determine which of these pairs of distributions may be significantly different.

Acute scenario KS tests.

```{r}
ks.test(x = acute_variability_stats$`0.1`, y = acute_variability_stats$unadjusted)
ks.test(x = acute_variability_stats$`1`, y = acute_variability_stats$unadjusted)
ks.test(x = acute_variability_stats$`2`, y = acute_variability_stats$unadjusted)
```

The periodic scenario.

```{r}
periodic_variability_stats <- data.table('individual' = 1:101,
                                         '0.1' = sapply(periodic_standard_variability$`0.1`$numeric, function(t) {max(t$AUC)}),
                                         '1' = sapply(periodic_standard_variability$`1`$numeric, function(t) {max(t$AUC)}),
                                         '2' = sapply(periodic_standard_variability$`2`$numeric, function(t) {max(t$AUC)}),
                                         'unadjusted' = sapply(simulation_periodic_standard_average$numeric, function(t) {max(t$AUC)}))

periodic_variability_long <- tidyr::pivot_longer(periodic_variability_stats, cols = -1)

summary(periodic_variability_stats[, 2])
summary(periodic_variability_stats[, 3])
summary(periodic_variability_stats[, 4])
summary(periodic_variability_stats[, 5])

ggplot(periodic_variability_long, aes(x = value, y = name, color = name, fill = name)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC value') + labs(fill = 'Time resolution in days', color = 'Time resolution in days')
```

Periodic scenario KS tests.

```{r}
ks.test(x = periodic_variability_stats$`0.1`, y = periodic_variability_stats$unadjusted)
ks.test(x = periodic_variability_stats$`1`, y = periodic_variability_stats$unadjusted)
ks.test(x = periodic_variability_stats$`2`, y = periodic_variability_stats$unadjusted)
```

And finally for the constant scenario.

```{r}
constant_variability_stats <- data.table('individual' = 1:101,
                                         '0.1' = sapply(constant_standard_variability$`0.1`$numeric, function(t) {max(t$AUC)}),
                                         '1' = sapply(constant_standard_variability$`1`$numeric, function(t) {max(t$AUC)}),
                                         '2' = sapply(constant_standard_variability$`2`$numeric, function(t) {max(t$AUC)}),
                                         'unadjusted' = sapply(simulation_constant_standard_average$numeric, function(t) {max(t$AUC)}))

constant_variability_long <- tidyr::pivot_longer(constant_variability_stats, cols = -1)

summary(constant_variability_stats[, 2])
summary(constant_variability_stats[, 3])
summary(constant_variability_stats[, 4])
summary(constant_variability_stats[, 5])

ggplot(constant_variability_long, aes(x = value, y = name, color = name, fill = name)) + ggridges::geom_density_ridges(alpha = 0.5) + xlab('AUC value') + labs(fill = 'Time resolution in days', color = 'Time resolution in days')
```

Constant scenario.

```{r}
ks.test(x = constant_variability_stats$`0.1`, y = constant_variability_stats$unadjusted)
ks.test(x = constant_variability_stats$`1`, y = constant_variability_stats$unadjusted)
ks.test(x = constant_variability_stats$`2`, y = constant_variability_stats$unadjusted)
```


We compute the effects of varying time resolution on the same chemical exposure scenario for a single chemical.

```{r}
time_resolution_acute_standard_response <- compute_time_resolution_sensitivity(chem.cas = '87-86-5', C_ext = acute_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1, resolutions = c(0.1, 1, 2), sample = 'left')
time_resolution_periodic_standard_response <- compute_time_resolution_sensitivity(chem.cas = '87-86-5', C_ext = periodic_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1, resolutions = c(0.1, 1, 2), sample = 'left')
time_resolution_constant_standard_response <- compute_time_resolution_sensitivity(chem.cas = '87-86-5', C_ext = constant_dose_matrix, model_parameters = pbtk_param, hill_params = hill_params_bpa, IR = 1, resolutions = c(0.1, 1, 2), sample = 'left')
```

Plot the sensitivity for the different scenarios.

Acute exposure.

```{r}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

Periodic exposure.

```{r}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

Constant exposure.

```{r}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

We also plot the signed versions of these sensitivity analyses.

Acute exposure.

```{r}
# Process the data
resolution_sensitivity_acute_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_acute_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_acute_standard_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_acute_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_acute_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```

Periodic exposure.


```{r}
# Process the data
resolution_sensitivity_periodic_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_periodic_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_periodic_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_periodic_standard_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_periodic_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_periodic_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_periodic_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```

Constant exposure.

```{r}
# Process the data
resolution_sensitivity_constant_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_constant_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_constant_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_constant_standard_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_constant_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_constant_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_constant_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```


We also examine the effects of varying the time resolution on the mixture sensitivity.

```{r}
time_resolution_mixture_response <- compute_time_resolution_sensitivity(chem.cas = c('87-86-5', '80-05-7'), C_ext = mixture_c_ext, model_parameters = pbtk_param, hill_params = hill_params_mix, IR = 1, resolutions = c(.1, 1, 2), sample = 'left')
```
We examine the results.

```{r}
# For the 0.1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_mixture_response$`0.1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 1 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_mixture_response$`1`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')

# For the 2 day resolution
ggplot(tidyr::pivot_longer(data.table(time_resolution_mixture_response$`2`[[1]])[, lapply(.SD, function(t) {abs(diff(t))}), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
         dplyr::filter(!is.na(value) & value >= 1E-15), aes(x = log10(value), y = name)) + 
  ggridges::geom_density_ridges() + 
  xlab('log10 absolute difference in response')
```

And again we examine the signed versions.

```{r}
# Process the data
resolution_sensitivity_mixture_signed_0.1 <- tidyr::pivot_longer(data.table(time_resolution_mixture_response$`0.1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_mixture_signed_1 <- tidyr::pivot_longer(data.table(time_resolution_mixture_response$`1`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

resolution_sensitivity_mixture_signed_2 <- tidyr::pivot_longer(data.table(time_resolution_mixture_response$`2`[[1]])[, lapply(.SD, diff), .SDcols = 2:5][, sample := 1:.N], cols = !sample) |> 
  dplyr::mutate(increment = abs(value), sign = ifelse(value > 0, 'positive', 'negative')) |>
  dplyr::filter(!is.na(increment) & increment >= 1E-15)

# Plot the data
ggplot(resolution_sensitivity_mixture_signed_0.1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_mixture_signed_1, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
ggplot(resolution_sensitivity_mixture_signed_2, aes(x = log10(increment), y = name, color = sign, fill = sign)) + ggridges::geom_density_ridges(alpha = .5)
```



```{r}
devtools::session_info()
```

